%-------------------------
% Resume in Latex
% Author: Arjun Vijay Prakash
% Based on template by Sourabh Bajaj
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{setspace}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.52in}
\addtolength{\evensidemargin}{-0.52in}
\addtolength{\textwidth}{1.04in}
\addtolength{\topmargin}{-.62in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setstretch{1.07}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=3pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://arjuncodess.is-a.dev/}{\Large Arjun Vijay Prakash}} & Email: \href{mailto:arjunv.prakash12345@gmail.com}{arjunv.prakash12345@gmail.com}\\
  \href{https://github.com/arjuncodess}{https://github.com/arjuncodess} $|$ \href{https://arjuncodess.is-a.dev/}{arjuncodess.is-a.dev} & Mobile: +91 8601404303 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://cmseducation.org/}{City Montessori School}}{Lucknow, India}
      {High School (11th \& 12th Grade), ISC Board}{Apr 2026 -- Apr 2028}
      \resumeItemListStart
        \resumeItem{Coursework}
          {Artificial Intelligence, Mathematics, Physics, Chemistry; ICSE Class 10 Board Score: 95.4\%.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{https://www.lodhageniusprogramme.com/}{Lodha Genius -- Ashoka University Programme}}{Ashoka University}
      {Selected Cohort Member, Science Track}{May 2026 -- June 2026}
      \resumeItemListStart
        \resumeItem{Programme}
          {Residential science and research programme with advanced math, science, and faculty-led sessions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Synthica}{Remote}
      {Associate Editor, Computer Science}{May 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Selection}
          {Selected from 400+ applicants; 47 associate editors chosen across 8 categories.}
        \resumeItem{Editorial Review}
          {Reviewing computer science research submissions and evaluating technical quality for peer review.}
      \resumeItemListEnd

    \resumeSubheading
      {City Montessori School}{Lucknow, India}
      {Vice President, HackSpace}{May 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Leadership}
          {Leading HackSpace, a student-run technology club for software development and hardware projects.}
        \resumeItem{Workshops \& Projects}
          {Organising sessions across apps, web, games, Arduino, robotics, and 3D modelling.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://github.com/pilot-ops-crm}{Pilot}}{Remote}
      {Chief Technology Officer (CTO)}{July 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Technical Leadership}
          {Leading development of an AI-powered Instagram automation platform for creators. Managing DM automation, lead responses, and deal tracking.}
        \resumeItem{Architecture \& Stack}
          {Architected the full-stack app with Next.js, React, Node.js, PostgreSQL, Instagram API, and Gemini API.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://dev.to/arjuncodess}{Technical Writer}}{Remote}
      {Freelance Technical Writer}{July 2025 -- Present}
      \resumeItemListStart
        \resumeItem{DEV.to}
          {Built 35,000+ followers and 410,000+ views by writing about web development, AI, and programming.}
        \resumeItem{Earnings}
          {Earned \$2,450 through technical writing, including \$1,375 in 2025 and \$500 from the Runner H AI Challenge.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/ArjunCodess/men2-predictor}{MEN2 Predictor} (\href{https://insef.org/insef/INSEF_Regional_Fair_Online_2025_26_Results.htm}{INSEF Bronze})}
      {Medical ML pipeline for MEN2 syndrome: 97.20\% accuracy and 100\% sensitivity across 152 patients and 20 studies.}
    \resumeSubItem{\href{https://github.com/ArjunCodess/analyzr}{Analyzr} (\href{https://www.producthunt.com/products/analyzr-2/launches/getanalyzr}{200+ Product Hunt Upvotes})}
      {Open-source analytics with one-line setup, real-time tracking, custom events, Discord alerts, and performance monitoring. Built with Next.js, Supabase, and TypeScript.}
    \resumeSubItem{\href{https://github.com/ArjunCodess/WebCrawlAI}{WebCrawlAI} (119 Stars)}
      {Gemini-powered scraping for dynamic websites, CAPTCHAs, and JSON extraction. Built with Python, Flask, Selenium, and Thordata.}
    \resumeSubItem{\href{https://github.com/ArjunCodess/chemistrycheck}{ChemistryCheck}}
      {RAG-based chat analysis for WhatsApp, Telegram, and Instagram exports. Built with Next.js, Drizzle ORM, Better Auth, and Gemini API.}
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{Harvard CS50 Series}
      {Completed \href{https://cs50.harvard.edu/certificates/0b5006d6-7765-4383-b72d-adc7067786c0}{CS50x}, \href{https://cs50.harvard.edu/certificates/ce13e906-e90f-4469-b1aa-ff24e88fa4be}{CS50T}, Ready Player 50, and CS50x Puzzle Day 2024/2025 Gold certificates.}
    \resumeSubItem{FreeCodeCamp Certifications}
      {\href{https://www.freecodecamp.org/certification/arjuncodess/responsive-web-design}{Responsive Web Design}, \href{https://www.freecodecamp.org/certification/arjuncodess/front-end-development-libraries}{Front-End Development Libraries}, and \href{https://www.freecodecamp.org/certification/arjuncodess/college-algebra-with-python-v8}{College Algebra with Python}.}
    \resumeSubItem{Competitions}
      {Top 25 in Xavier University's Invisible Wars Cyber Defense Challenge; Top 100 at HACKHAZARDS.}
    \resumeSubItem{YC Startup School India}
      {Confirmed attendee for Y Combinator's Bangalore event.}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
\vspace{1pt}
\small{
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}>{\raggedright\arraybackslash}p{0.31\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}}
\textbf{Web / App} & \textbf{AI / Data} & \textbf{Embedded / Hardware} \\
TypeScript, React, Next.js, Node.js, PostgreSQL, MongoDB, Supabase, Tailwind CSS &
Python, scikit-learn, XGBoost, LightGBM, SHAP, pandas, NumPy, Gemini API &
ESP32, Arduino C++, I2C OLED, rotary encoder, DHT11, MQ-135, Wi-Fi/NTP, robotics, 3D modelling \\
\textbf{Research / Editorial} & \textbf{Leadership / Community} & \\
Research writing, peer review, editorial standards, technical writing &
Team management, workshop planning, club leadership & \\
\end{tabular*}
}

%-------------------------------------------
\end{document}
